Automatic Summarization of Scientific Texts

### 2018-06-10 paper/paper.tex
Modified gitignore

Thanks to the open policy of arXiv we were able to collect our own dataset of scientific papers from \textit{stat.ML} category. We publish it together with this paper an encourage everyone to use it as they like in their own projects.

@@

Our dataset contains 2000 documents (papers). Each one of them is represented by a row with three properties:

@@

Evaluating a summary is a difficult task because there does not exist an ideal summary for a given document or set of documents. \cite{das-7}. Manual evaluation is too expensive, so we will only be considering the automatic techniques.

@@

>>>>

Thanks to the open policy of arXiv we were able to collect our own dataset of scientific papers from \textit{stat.ML} category\footnote{\url{https://arxiv.org/list/stat.ML/recent}}. We publish it together with this paper an encourage everyone to use it as they like in their own projects.

@@

Our dataset contains 2000 documents (papers). Each one of them is represented by a row with the following properties:

@@

Evaluating a summary is a difficult task because there is no single summary that would be ideal for a given document. In most cases even human evaluators can not agree on which of the given summaries is better.\cite{das-7}. Unlike other NLP problems, like translation or parsing, when it comes to text summarization we can not clearly define what makes a summary good or bad. Manual evaluation of summaries is too expensive, so in the following sections we will only consider automatic techniques.

@@

\subsection{ROUGE}
